---
title: "Project1"
author: "Subhalaxmi Rout"
date: "2/23/2020"
output:
  pdf_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project Instruction
In this project, you’re given a text file with chess tournament results where the information has some structure. Your job is to create an R Markdown file that generates a .CSV file (that could for example be imported into a SQL database) with the following information for all of the players:
Player’s Name, Player’s State, Total Number of Points, Player’s Pre-Rating, and Average Pre Chess Rating of Opponents
For the first player, the information would be:
Gary Hua, ON, 6.0, 1794, 1605
1605 was calculated by using the pre-tournament opponents’ ratings of 1436, 1563, 1600, 1610, 1649, 1663, 1716, and dividing by the total number of games played.
If you have questions about the meaning of the data or the results, please post them on the discussion forum. Data science, like chess, is a game of back and forth…
The chess rating system (invented by a Minnesota statistician named Arpad Elo) has been used in many other contexts, including assessing relative strength of employment candidates by human resource departments.


```{r eval=TRUE}
#load library
#install.packages("stringr")
#install.packages("RMySQL")
#install.packages('tinytex')
#tinytex::install_tinytex()
library("stringr")
library(RMySQL)
data1 <- "tournament.txt"
data1 <- readLines(data1)
data1

#remove "--" from data
line <- str_detect(data1,"\\-----------------------------------------------------------------------------------------")
chess_data <- data1[!line]
chess_data
```

### Extract player's id
```{r}
id_pattern <- "\\d{1,2}\\s(?=\\|)"
ply_id <- unlist(str_extract_all(unlist(chess_data), id_pattern))
ply_id
length(ply_id)
```

### Extract player's name
```{r}
#extract names of all players
name_pattern <- "([A-Z]+\\s){2,3}"
ply_names <- unlist(str_extract_all(unlist(chess_data), name_pattern))
ply_names <- ply_names[2:length(ply_names)]
ply_names
length(ply_names)
```
### Extract player's state
```{r}
state_pattern <- "([A-Z]){2}\\s(?=\\|)"
states <- unlist(str_extract_all(unlist(chess_data), state_pattern))
head(states, 10)
length(states)
```

### Extract player's total number of points
```{r}
points_pattern <- "\\d\\.\\d"
total_points <- unlist(str_extract_all(unlist(chess_data), points_pattern))
head(total_points,10)
length(total_points)
```

### Extract player's pre-rating
```{r}
pre_rating_pattern <- "(?<!\\>\\s)(?<=\\s{1,2}|\\s\\:)(\\d{3,4}(?=\\s|P))"
pre_rating <- unlist(str_extract_all(unlist(chess_data), pre_rating_pattern))
pre_rating
length(pre_rating)
```

### Calculate Average pre-rating
```{r}
rounds_pattern <- "(\\d{1,2}|[[:space:]]{1})(?=\\|)"
player_opponents <- unlist(str_extract_all(unlist(chess_data), rounds_pattern))
player_opponents[player_opponents==" "]  = 0
#length(player_opponents)
#player_opponents
round1 <- as.numeric(player_opponents[seq(16, length(player_opponents), 20)])
round1

round2 <- as.numeric(player_opponents[seq(17, length(player_opponents), 20)])
round2

round3 <- as.numeric(player_opponents[seq(18, length(player_opponents), 20)])
round3

round4 <- as.numeric(player_opponents[seq(19, length(player_opponents), 20)])
round4

round5 <- as.numeric(player_opponents[seq(20, length(player_opponents), 20)])
round5


round6 <- as.numeric(player_opponents[seq(21, length(player_opponents), 20)])
round6

round7 <- as.numeric(player_opponents[seq(22, length(player_opponents), 20)])
round7

player_opponents <- matrix(c(round1, round2, round3, round4, round5, round6, round7),nrow = 64, ncol = 7)
#player_opponents
avg_pre_rating = 0
for (i in 1:64)
{
  avg_pre_rating[i] <- round(mean(as.numeric(pre_rating[player_opponents[i,]]), na.rm = TRUE),0)
}
avg_pre_rating
```
### Creat table
```{r}
tournament_table <- data.frame(ply_id,ply_names, states, total_points, pre_rating, avg_pre_rating)
head(tournament_table)
```
### Export data to CSV
```{r}
write.csv(tournament_table, file = "TournamentTable.csv")
```

### Connect to Mysql

```{r}
db_user <- 'root'
db_password <- 'root'
db_name <- 'tournament'
db_host <- 'localhost'
db_port <- 3306
mydb <- dbConnect(MySQL(), user = db_user, password = db_password, dbname = db_name, host = db_host, port = db_port)
dbListTables(mydb)
dbReadTable(mydb, "tournament")
```

### Load data to MySQL
```{r}
dbSendQuery(mydb, "SET GLOBAL local_infile = true;")
dbWriteTable(conn = mydb, name = 'tournament', value = as.data.frame(tournament_table), overwrite = TRUE)
```
### Query from Mysql DB

```{r}
sql <- "select * from tournament limit 5";
result <- dbGetQuery(mydb, sql);
knitr::kable(
  head(result),
  caption = "dbGetQuery result set [head]")
```